CF Registry Analysis

### 2022-12-27 Christine Chan/CF Registry/cf_registry_analysis.qmd
Update cf_registry_analysis.qmd

```{r}
#| label: tbl-screening_ogtt
#| tbl-cap: "Yearly OGTT Screening Rates"
year_screen = function(df=encounter,year){
  # Filter and count
  inc = df %>% 
    filter(reviewyear==year,first_cfrd_both >= year) %>%
    mutate(ogtt = !(is.na(ogttfast_bloodglucose) | is.na(twohour_bloodglucose))) %>%
    group_by(eDWID) %>%
    summarise(ogtt = max(ogtt),`Age Group` = `Age Group`[1])
  inc = inc %>% group_by(ogtt) %>% count(`Age Group`) %>% filter(`Age Group` != "< 10")
  # Calculations
  total_screened = sum(inc$n[inc$ogtt==1])
  total_seen = sum(inc$n)
  screen_rate = total_screened/total_seen * 100

@@

```{r}
#| label: tbl-screening_a1c
#| tbl-cap: "Yearly HbA1c Screening Rates"
year_screen = function(df=encounter,year){
  # Filter and count
  inc = df %>% 
    filter(reviewyear==year,first_cfrd_both >= year) %>%
    mutate(a1c = !is.na(hgba1c)) %>%
    group_by(eDWID) %>%
    summarise(a1c = max(a1c),`Age Group` = `Age Group`[1])
  inc = inc %>% group_by(a1c) %>% count(`Age Group`) %>% filter(`Age Group` != "< 10")
  # Calculations
  total_screened = sum(inc$n[inc$a1c==1])
  total_seen = sum(inc$n)
  screen_rate = total_screened/total_seen * 100

@@

In @tbl-screening_ogtt and @tbl-screening_a1c, people with CFRD (by either registry definition or OGTT) and those under age 10 were excluded. Screening rate is calculated as the number of people with an OGTT divided by the total number of people seen in clinic that year.

>>>>

```{r}
#| label: tbl-screening_ogtt
#| tbl-cap: "Yearly OGTT Screening Rates"
year_screen = function(df=encounter,year){
  # Filter and count
  inc = df %>% 
    filter(reviewyear==year,first_cfrd_cffpr > year | is.na(first_cfrd_cffpr)) %>%
    mutate(ogtt = !is.na(ogttfast_bloodglucose) | !is.na(twohour_bloodglucose)) %>%
    group_by(eDWID) %>%
    summarise(ogtt = max(ogtt),`Age Group` = `Age Group`[1])
  inc = inc %>% group_by(ogtt) %>% count(`Age Group`) %>% filter(`Age Group` != "< 10")
  # Calculations
  total_screened = sum(inc$n[inc$ogtt==1])
  total_seen = sum(inc$n)
  screen_rate = total_screened/total_seen * 100

@@

```{r}
#| label: tbl-screening_a1c
#| tbl-cap: "Yearly HbA1c Screening Rates"
year_screen = function(df=encounter,year){
  # Filter and count
  inc = df %>% 
    filter(reviewyear==year,first_cfrd_cffpr > year | is.na(first_cfrd_cffpr)) %>%
    mutate(a1c = !is.na(hgba1c)) %>%
    group_by(eDWID) %>%
    summarise(a1c = max(a1c),`Age Group` = `Age Group`[1])
  inc = inc %>% group_by(a1c) %>% count(`Age Group`) %>% filter(`Age Group` != "< 10")
  # Calculations
  total_screened = sum(inc$n[inc$a1c==1])
  total_seen = sum(inc$n)
  screen_rate = total_screened/total_seen * 100

@@

In @tbl-screening_ogtt and @tbl-screening_a1c, people with CFRD (by registry definition) and those under age 10 were excluded. Screening rate is calculated as the number of people with an OGTT divided by the total number of people seen in clinic that year.
